### 2023-02-02 manuscript.tex
all the citations. Bioschemas by article. [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/1cbe9b42e4c7f0fecfd786fcff5fbd152fe3abdb.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/1cbe9b42e4c7f0fecfd786fcff5fbd152fe3abdb/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4076291242

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/7dd90cbf606ec18cbbd096a79baebdf28c4abed6/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/7dd90cbf606ec18cbbd096a79baebdf28c4abed6}{stain/2022-fdo-paper@7dd90cb}
on February 2, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/1cbe9b42e4c7f0fecfd786fcff5fbd152fe3abdb/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/1cbe9b42e4c7f0fecfd786fcff5fbd152fe3abdb}{stain/2022-fdo-paper@1cbe9b4}
on February 2, 2023.
